Name matching through deep learning

### 2018-11-19 old/paper2018/samplepaper.tex
wording

%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Merging datasets frequently requires joining across columns that have
different surface forms for the same entity (e.g., the name of a
person might be represented as \textit{Douglas Adams} or
\textit{Adams, Douglas}).  However, data management systems are currently limited
to performing merges based on string equality, or at best using
string similarity.  We propose an approach to name matching based on deep learning models.  
Our approach depends on (a) creating
a deep learning model that maps alternate forms for the same entity into vector space such that alternate forms are closest, (b) indexing these vectors using a nearest
neighbors algorithm to find the forms that can be potentially joined
together.  To build these models, we had to adapt techniques from
metric learning due to the characteristics of the data; specifically we describe 
novel sample selection techniques and loss functions that work for this problem.  
To evaluate our approach, we used Wikidata as ground truth
and built models from datasets with approximately 1.1M people's names
(200K identities) and 130K company names (70K identities).  We developed models that 
allow for joins with precision@1 of .75-.81 and
recall of .74-.81.  We make the models available for aligning people or companies across multiple datasets.

>>>>

%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Merging datasets frequently requires joining across columns that have
different surface forms for the same entity (e.g., the name of a
person might be represented as \textit{Douglas Adams} or
\textit{Adams, Douglas}).  However, data management systems are currently limited
to performing merges based on string equality, or at best using
string similarity.  We propose an approach to name matching based on deep learning models.  
Our approach depends on (a) creating
a deep learning model that maps alternate forms for the same entity into vector space such that alternate forms are closest, (b) indexing these vectors using a nearest
neighbors algorithm to find the forms that can be potentially joined
together.  To build these models, we adapted techniques from
metric learning to the characteristics of the data; specifically we describe 
novel sample selection techniques and loss functions that work for this problem.  
To evaluate our approach, we used Wikidata as ground truth
and built models from datasets with approximately 1.1M people's names
(200K identities) and 130K company names (70K identities).  We developed models that 
allow for joins with precision@1 of .75-.81 and
recall of .74-.81.  We make the models available for aligning people or companies across multiple datasets.
